Using numerical modelling to investigate temperature and wave exposure as drivers

### 2019-10-09 morphology_paper.Rmd
added extra paragraph to temperature results section

The mean annual coastal water temperature for the study sites located on the western side of the peninsula ranged from 14.5 ± 0.9 ℃ (mean ± SD) at St. Helena Bay, the most northern site on the western side of the peninsula, to 14.6 ± 0.3 ℃ at Olifantsbos, the most southern site on the western side of the peninsula (see figure \ref{fig:Temperature variables plot}A). For sites located on the eastern side of the peninsula (within False Bay), the annual mean coastal water temperatures ranged from 15.5 ± 0.9 ℃ at Buffelsbaai to 15.0 ± 0.9 ℃ at Betty’s Bay, the most eastern site on the coastline in this study (see figure \ref{fig:Temperature variables plot}A). Oudekraal had the lowest annual mean coastal water temperature of 12.3 ± 0.9. Annual maximum coastal temperatures for study sites located on the western side of the peninsula ranged from 16.3 ℃ at St. Helena Bay to 15.1 ℃ at Olifantsbos. For sites located east of the peninsula, annual maximum coastal water temperatures ranged from 16 ℃ at Buffelsbaai to 16.5 ℃ at Betty’s Bay. Amongst all sites, Kalk Bay had the highest annual maximum temperature of 19 ℃. Annual minimum coastal water temperatures for the study sites on the western side of the peninsula ranged from 12.9 ℃ at St. Helena Bay to 14.1 ℃ at Olifantsbos, and on the western side of the peninsula ranged from 15.0 ℃ at Buffelsbaai to 13.6 ℃ at Betty’s Bay.  The annual range in temperature on the western side on the peninsula was 3.4 at St. Helena Bay to 0.9 at Olifantsbos, and on the eastern side on of the peninsula was 1.0 at Buffelsbaai to 2.9 at Betty’s Bay. As can be seen in figure \ref{fig:Temperature variables plot}A, the trend in the range of temperature decreases from St. Helena Bay to Miller’s point and then increases from Kalk Bay to Betty’s Bay. Also, annual range in temperatures within False Bay are larger in winter (August) compared to summer (February).

@@

>>>>

The mean annual coastal water temperature for the study sites located on the western side of the peninsula ranged from 14.5 ± 0.9 ℃ (mean ± SD) at St. Helena Bay, the most northern site on the western side of the peninsula, to 14.6 ± 0.3 ℃ at Olifantsbos, the most southern site on the western side of the peninsula (see figure \ref{fig:Temperature variables plot}A). For sites located on the eastern side of the peninsula (within False Bay), the annual mean coastal water temperatures ranged from 15.5 ± 0.9 ℃ at Buffelsbaai to 15.0 ± 0.9 ℃ at Betty’s Bay, the most eastern site on the coastline in this study (see figure \ref{fig:Temperature variables plot}A). Oudekraal had the lowest annual mean coastal water temperature of 12.3 ± 0.9. Annual maximum coastal temperatures for study sites located on the western side of the peninsula ranged from 16.3 ℃ at St. Helena Bay to 15.1 ℃ at Olifantsbos. For sites located east of the peninsula, annual maximum coastal water temperatures ranged from 16 ℃ at Buffelsbaai to 16.5 ℃ at Betty’s Bay. Amongst all sites, Kalk Bay had the highest annual maximum temperature of 19 ℃. Annual minimum coastal water temperatures for the study sites on the western side of the peninsula ranged from 12.9 ℃ at St. Helena Bay to 14.1 ℃ at Olifantsbos, and on the western side of the peninsula ranged from 15.0 ℃ at Buffelsbaai to 13.6 ℃ at Betty’s Bay.  The annual range in temperature on the western side on the peninsula was 3.4 at St. Helena Bay to 0.9 at Olifantsbos, and on the eastern side on of the peninsula was 1.0 at Buffelsbaai to 2.9 at Betty’s Bay.

@@

In general, the mean temperature increases for sites located within False Bay and sites located within False Bay also exibited less variation around the mean temperature compared to sites on the western side of the peninsula(\ref{fig:Temperature variables plot}A). This is verified by \ref{fig:Temperature variables plot}B, which shows a significanlty lower (p<0.05) median temperature and less variation in temperature for sites located on the western side of the peninsula compared to sites on the eastern side.
